Codebook created on 2021-11-05 at 2021-11-05 13:07:36

### 2021-12-16 codebooks/codebook_us.Rmd

---
title: "Codebook created on 2021-11-05 at 2021-11-05 12:56:18"
output: github_document
---

@@

## Dataset description
The data contains 552 cases and 31 variables.

@@

```{r}
summaries <- read.csv("./codebook_dk.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2021-11-05 at 2021-11-05 13:07:36"
output: github_document
---

@@

## Dataset description
The data contains 518 cases and 33 variables.

@@

```{r}
summaries <- read.csv("./codebook_us.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```
